\textbf{Emergency Service Location Optimization in a Multi-Zone County based on Population Distribution}

### 2013-11-16 LaTeX/paper.tex
Fixed ref bug

\usepackage{url}
\usepackage{caption}
% \usepackage{fullpage}
\usepackage{fancyhdr}
\usepackage{amsmath}
\usepackage{subcaption}
\usepackage{float}
\restylefloat{table}
\restylefloat{figure}
\usepackage{setspace}
% \usepackage{minted}
% \usemintedstyle{colorful}
\graphicspath{{./Pictures/}}

@@

First and foremost, if you look at Zone 2, you see two paths going out to Zones 1 and 3, respectively. Because of the short travel time it takes to get to both of the zones, the reach of an ambulance coming out of Zone 5 is slightly larger, and you are more likely to save more people. Furthermore, the overall population density of the three zones (1+2+3) is large, weighing Zone 2 as one of the more important nodes on the graph. Therefore, intuitively, Zone 2 makes sense as a starting point.

@@

Finally, if you look at Zone 3, you see that while though redundant, the overall population covered by having an ambulance stationed there is the next greatest. For that reason, it makes the most sense to place the third ambulance in Zone 3.

@@

>>>>

\usepackage{url}
% \usepackage{fullpage}
\usepackage{fancyhdr}
\usepackage{amsmath}
\usepackage{subcaption}
\usepackage{float}
\restylefloat{table}
\restylefloat{figure}
\usepackage{setspace}
% \usepackage{minted}
% \usemintedstyle{colorful}
\graphicspath{{./Pictures/}}

@@

First and foremost, if you look at Zone 2, you see two paths going out to Zones 1 and 3, respectively. Because of the short travel time it takes to get to both of the zones, the reach of an ambulance coming out of Zone 2 is slightly larger, and you are more likely to save more people. Furthermore, the overall population density of the three zones (1+2+3) is large, weighing Zone 2 as one of the more important nodes on the graph. Therefore, intuitively, Zone 2 makes sense as a starting point.

@@

Finally, if you look at Zone 1, you see that while though redundant, the additional population covered by having an ambulance stationed there is the next greatest. For that reason, it makes the most sense to place the third ambulance in Zone 1.

@@

For each of these scenarios, our greedy heuristic got the exact same answer as the
brute-force algorithm as well as the intuitive solution from the graph. Because our greedy heuristic found the same answer as the brute-force algorithm (which looked for the ideal, optimal answer) our greedy heuristic seems to be performing efficiently and accurately.
